That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-23 ms.tex
bbl

\section{Conclusion}
In this work, we presented an independent analysis of HST observations of the Kepler-1625 system. In contrast to previous analysis by \citep{teachey18b}, we do not find evidence for the transit of a moon.

what is 
approach to data reduction was very similar, but of the data reduction, and

>>>>

\section{Discussion}
As discussed above, we do not recover the moon. Our analysis was designed to be independent, and as such makes different choices about the data reduction and the choice of sytematics model.

We explored several avenues to determine what caused the difference in our results. We first checked whether the detrending model was responsible.

We also compared the data directly (see Figure\,\ref{fig:raw}). The data is different!
rotate the image, aperture choice, measurement of the background, outlier masking,

In this work, we presented an independent analysis of HST observations of the Kepler-1625 system. In contrast to previous analysis by \citep{teachey18b}, we do not find evidence for the transit of a moon. We obtain a better fit to the data without including a moon in the model.  We
